Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex
Mejorando la legibilida de las graficas

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\caption{Information about the bug as displayed by Gerrit.}
\label{fig:parentgerrit}       % Give a unique label
\end{figure}

@@

\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{manyprevious.png}
\caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}
\label{fig:manyprevious}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{addedlines.png}
\label{fig:added}       % Give a unique label
\caption{Example of scenario where the bug fix is composed only of lines added. The fix bug commit with lines added in green can be seen on the left (subfigure (1)), and the file as it was before the fix bug commit on the right (subfigure (2)).}
%52919
\end{figure}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}}\gema{he creado esta pagina en github para el paquete de reproducibilidad http://gemarodri.github.io/2016-msr-prevcommit/} including data sources, intermediate data and scripts that can be obtained.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[height=1.9cm]{parent.png}
\caption{Information about the bug as displayed by Gerrit.}
\label{fig:parentgerrit}       % Give a unique label
\end{figure}

@@

%\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
%\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}

\begin{figure*}[ht]
\centering
\includegraphics[height=4cm]{manyprevious.png}
\caption{Example of previous commit where more than one commit has been identified. On the left, the file after the bug-fixing commit. Previous commit \textit{e5296c1da} (middle) is the cause of the bug in line 2422 with the presence of an incorrect \texttt{break} statement. 
Previous commits \textit{e7be0a988} (right) has also been identified; however, as it just changes the version number (line 218), it can be classified as not causing the bug.}
\label{fig:manyprevious}       % Give a unique label
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=3.6cm]{addedlines.png}
\label{fig:added}       % Give a unique label
\caption{Example of scenario where the bug fix is composed only of lines added. The fix bug commit with lines added in green can be seen on the left (subfigure (1)), and the file as it was before the fix bug commit on the right (subfigure (2)).}
%52919
\end{figure*}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gemarodri.github.io/2016-msr-prevcommit/}} including data sources, intermediate data and scripts that can be obtained.
